\documentclass{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.5in, right=0.5in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\begin{document}
	\begin{center}
		\thispagestyle{empty}
		\large \textbf{Jesús Molina Roldan\\}
		\normalsize jmr\textunderscore sultan@hotmail.com $\mid$ 697656469 $\mid$ \href{https://jesu20950.github.io/}{jesu20950.github.io} \\ 
		\hrulefill
	\end{center}
	
	\noindent \textbf{\underline{WORK EXPERIENCE}} \\
	\noindent \textbf{Everis} \hfill Barcelona, Spain \\
	\textit{Full stack developer, Insurance Department} \hfill 2019-2020 \\
	I was an intern working with the Mutua de Propietarios company. My tasks consisted of programming and testing services on a web page.
	\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
		\item {\textbf{Programming languages:} Java, JavaScript, SQL, HTML.}\\
	\end{itemize}
	

	\noindent \textbf{\underline{EDUCATION}} \\
	\textbf{Maristes Champagnat of Badalona} \\
	\textit{Bachelor + Technological}  \hfill 2014-2016  \\ \\
	\textbf{Polytechnic University of Catalonia} \\
	\textit{Degree in Informatics Engineering + Computing}  \hfill 2016-Present \\
	

	\noindent \textbf{\underline{TECHNICAL SKILLS}} \\
	\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
		\item {\textbf{Operating system:} Windows and Linux OSs.}
		\item {\textbf{Programming languages:} C, C++, Matlab, Java, JavaScript, SQL, HTML, CSS}
		\item {\textbf{Data Science:} R, Python with NumPy and Pandas}
		\item {\textbf{Version control:} Git, Github}\\
	\end{itemize}
	
		\noindent \textbf{\underline{PROJECTS}} \\
	\noindent \textbf{pqneon}  \hfill  Present \\
	Post-quantum library implementation with NEON instructions. \\


	\noindent \textbf{\underline{LANGUAGES}} \\
	\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
		\item {Spanish.}
		\item {Catalan.}
		\item {English. \\}
	\end{itemize}
	

	\noindent \textbf{\underline{EXTRA SECTION}} \\
	\noindent \textbf{Music:} Guitarist. \\
	\noindent Immediate availability.
	
	
\end{document}